---
title: "Document title"
output: html_document
date: "2023-01-28"
---

# R code chunks

This below is an R code chunk:

```{r}
data(mtcars)

plot(mtcars)
```


The code chunk above will appear in the final output. 
The code chunk below will be hidden:

```{r, echo = FALSE}
data(iris)

plot(iris)
```


This next code chunk will not be evaluated:

```{r, eval = FALSE}
data(titanic)

str(titanic)
```


The last one below runs, but code and output from the code is 
not shown in the final document. This is useful for loading 
libraries and hiding startup messages:

```{r, include = FALSE}
library(dplyr)
```


Here is an inline code chunk:
The iris dataset has `r nrow(iris)` rows.

This sentence has a footnote.^[This is the footnote]

This is an LaTeX equation:

\begin{align*}
S(\omega) 
&= \frac{\alpha g^2}{\omega^5} 
  e^{[ -0.74\bigl\{\frac{\omega U_\omega 19.5}{g}\bigr\}
   ^{\!-4}\,]} \\
&= \frac{\alpha g^2}{\omega^5} 
\exp\Bigl[ -0.74\Bigl\{\frac{\omega U_\omega 19.5}{g}\Bigr\}
  ^{\!-4}\,\Bigr] 
  
  
\end{align*}